\chapter{Prerequisites}
\section{Review of Measure Theory and Topology}
%set M^1(X) of all probability measures on the Borel-\sigma-Algebra of X
%M^1 with weak*-topology is compact

In this section we will remind the reader briefly of some definitions and results from measure theory and topology that will be of use later.

Throughout, we will use the following notation.
\begin{notation}Let $\Omega$ be a set.
	\begin{enumerate}
		\item Let $A\subset \Omega$ be a subset. Then $A^c$ denotes the complement of $A$ in $\Omega$.
		\item $\mathcal{P}(\Omega)$ shall denote the set of subsets of $\Omega$. 
	\end{enumerate}
\end{notation}
\noindent Recall the following definition as can be found in \cite{friedl:ana-3}.
%\begin{definition}
%	Let $\Omega$ be a set. We say $\mathcal{A}\subset \mathcal{P}(\Omega)$ is a \emph{set-algebra} on $\Omega$, if the following statements hold:
%	\begin{enumerate}
%		\item $\emptyset\in\mathcal{A}$,
%		\item $A\in \mathcal{A}\Rightarrow A^c\in \mathcal{A}$,
%		\item $A,B\in \mathcal{A}\Rightarrow A\cup B\in \mathcal{A}$
%	\end{enumerate}
%\end{definition}

\begin{definition}
	Let $\Omega$ be a set. We say $\mathcal{A}$ is a \emph{$\sigma$-Algebra on $\Omega$}, if the following statements are true:
	\begin{enumerate}
		\item $\emptyset\in \mathcal{A}$.
		\item $A\in \mathcal{A}\Rightarrow A^c\in \mathcal{A}$.
		\item The union of countably many sets in $\mathcal{A}$ is in $\mathcal{A}$.
	\end{enumerate}
\end{definition}

\begin{definition}
	For $S\subset\mathcal{P}(\Omega)$, we call 
	\[
	\langle S\rangle^\sigma:=\text{Intersection of all $\sigma$-Algebras on $\Omega$ that contain $S$}
	\]
	the $\sigma$-Algebra \emph{generated by} $S$.
\end{definition}

\begin{definition}
	Let $(X,\mathcal{T})$ be a topological space. We call the $\sigma$-Algebra generated by all open sets in $X$, i.e. $\mathcal{B}=\langle \mathcal{T} \rangle^\sigma$, the \emph{Borel-$\sigma$-Algebra}.
\end{definition}


\begin{definition}Let $\Omega$ be a set and $\mathcal{A}$ a $\sigma$-Algebra on $\Omega$. 
\begin{enumerate}%definition regular measure
%\item We call $(\Omega,\mathcal{A})$ a measure space.%todo no! measure space?
\item A function 
	\[
	\mu:\mathbb{A}\to \R\cup \{\pm\infty\}
	\]
	satisfying
	\begin{enumerate}
		\item $\mu(\emptyset)=0$
		\item For any pairwise disjoint family $(A_k)_{k\in\N}$  of sets in $\mathcal{A}$
		\[
		\mu\left(\bigcup_{k=1}^\infty A_k\right)=\sum_{k=1}^{\infty}\mu(A_k)
		\]	
	\end{enumerate}\enlargethispage{1cm}
is called a \emph{signed measure on $(\Omega,\mathcal{A})$}.

\item We say $\mu$ is a \emph{(positive) measure}, if it is a signed measure with the property 
\[
\mu(X)\geq 0\quad \forall X\in \mathcal{A}.
\]

\item Let $X$ be a Hausdorff space, $\mathcal{A}$ a $\sigma$-algebra with $\mathcal{B}\subset\mathcal{A}$.  We say $\mu$ is a \emph{(positive) regular measure} if it is a measure such that for all $A\in \mathcal{A}$
\[
\mu(A)=\inf\{\mu(U)\colon A\subset U, U \text{ open}\}=\sup\{\mu(K)\colon K\subset A, K\text{ compact} \}.
\] 
and we say $\mu$ is a \emph{signed regular measure} if 
\[
|\mu|(A):=\sup_{\mathfrak{D}}\sum_{E\in \mathfrak{D}}|\mu(E)|,
\]
is a positive regular measure, where the supremum is taken over all decompositions of $A$ into finitely many disjoint sets.

\item We say $\mu$ is a \emph{probability measure}, if it is a positive regular measure and
\[
\mu(\Omega)=1.
\]

\item We say $\mu$ is \emph{finite} if it does not take on the values $\pm\infty$ for any set.
\end{enumerate}
\end{definition}

\begin{notation}
	Let $X$ be a topological space and $\mathcal{B}(X)$ the Borel-$\sigma$-Algebra on $X$. We write
	\begin{enumerate}
	\item	$\M(X)=\{\mu\mid \mu$ is a finite, regular signed Borel measure on $X\}$.
	\item $\M^+(X)=\{\mu\mid \mu$ is a finite, regular Borel measure on $X\}$.
	\item $\M^1(X)=\{\mu\mid\mu$ is a Borel probability measure on $X \}$.
	\end{enumerate}
\end{notation}

We will equip $\M^1(X)$ with a suitable topology later (namely the weak*-topology).

Note that
\[
\M^1(X)\subset \M^+(X)\subset \M(X)
\]
In particular the following clearly holds.

\begin{lemma}
	Equipped with the usual operations of addition and scalar multiplication, the set $\M(X)$ is a real vector space, and the spaces $\M^+(X)$ and $\M^1(X)$ are convex subsets of $\M(X)$.
\end{lemma}

We now define a special kind of measures, namely those whose support is a singleton. 
\begin{definition}
	%A measure with finite support is called an \emph{atomic measure}. If the support consists of only one point, then such a (atomic) measure $\delta_x$ is called a \emph{Dirac measure}, in particular
	The measures assigning weight one to a single point are called \emph{Dirac measures}, i.e.
	\[
	\delta_x(A)=\begin{cases}
	1&\text{if }x\in A\\
	0&\text{if }x\not\in A
	\end{cases},
	\] 
	are called \emph{Dirac measures}.
\end{definition}
We will see in \autoref{thm:finite-support} that Dirac measures are important for approximating more general measures.

We conclude this review of measure theory with a reminder of the following theorem as can be found in \cite[Theorem 4.11, 4.13]{friedl:ana-3} or \cite[S.18]{cohn}
\begin{theorem}[Theorem of Carathéodory]\label{thm:measure-extension}
	Let $X$ be a set, let $\mu^\ast$ be an outer measure on $X$, and let $\mathcal{A}_{\mu^\ast}$ be the collection of all $\mu^\ast$-measurable subsets of $X$. Then
	\begin{enumerate}
		\item $\mathcal{A}_{\mu^\ast}$ is a $\sigma$-slgebra, and
		\item the restriction of $\mu^\ast$ to $\mathcal{A}_{\mu^\ast}$ is a measure on $\mathcal{A}_{\mu^\ast}$.
	\end{enumerate}	
\end{theorem}

%The following results are well known and therefore no proof will be given here. We refer the interested reader to \cite{friedl:ana3}.
%
%\begin{lemma}
%	There does not exist a measure on $\mathcal{P}(\R^n)$ for $n\in \N$.
%\end{lemma}

%\begin{definition}
%	A function $f: X\to \R$ is called measurable if the sets $f^{-1}(-\infty,a]$ are measurable for all $a\in \R$.
%\end{definition}

%\begin{lemma}
%	All real valued continuous functions are measurable.
%\end{lemma}

\input{topology}
